---
title: "R_workshop_2023"
output: html_document
date: "2023-10-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
## Open tidyverse library
```{r}
library(tidyverse)
```


# First we will get the dataset and load it into a dataframe

```{r}
kart <- read.csv("karts.csv")
```
 
## Lets examine the first 6 lines of the code
```{r}
head(kart)
```


# 1.Analysis of our data

  a. How many karts are in the dataset?
```{r}
nrow(kart)
```

  b. How many columns are in the dataset?
```{r}
#Solution for students to fill
ncol(kart)
```


  c. What are the column names?
```{r}
names(kart)
```

  d. Get the values stored in the acceleration column
```{r}
#Solution
kart$Acceleration
```

  e. Rename the column Body to Kart
```{r}
names(kart)[1] <- "Kart"
```

  f. Print out the first six rows from greatest to least acceleration
```{r}
kart <- arrange(kart, desc(Acceleration))
head(kart)
```
  
  g. Get the value in the third row and the fourth column
```{r}
#Solution for student
kart[3,4]
```

  h. Select only the rows that have a Acceleration of 5 and only print the Weight and Acceleration
```{r}
kart[kart$Acceleration==5,c("Weight", "Acceleration")]
```
  
# 2. Generating graphs using our dataset
  
  a. Generate a bar graph of the number of karts with each possible acceleration
```{r}
acc_counts <- as.data.frame(table(kart$Acceleration))

colnames(acc_counts) <- c("Acceleration", "Count")

ggplot(acc_counts, aes(x = Acceleration, y = Count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Number of Karts by Acceleration",
       x = "Acceleration",
       y = "Count") +
  theme_minimal()
```
  
  
  b. Make a similar bar graph for the number of karts for each weight category
```{r}
#Solution
weight_counts <- as.data.frame(table(kart$Weight))

# Rename the columns for clarity
colnames(weight_counts) <- c("Weight", "Count")

# Create a bar graph using ggplot2
ggplot(weight_counts, aes(x = Weight, y = Count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Number of Karts by Weight",
       x = "Weight",
       y = "Count") +
  theme_minimal()
```



# 3. Statistical tests



